Demographic Species Distribution Models

### 2019-10-11 manuscript/ms.Rmd
use probability lambda>1 as range, and tidy plot and table

name_lookup <- matrix(
  c("intercept", "intercept",
    "pcMix", "mixed forest cover",
    "pcDec", "deciduous forest cover",
    "pcCon", "coniferous forest cover",
    "bio1", "annual mean temperature",
    "bio6", "min temperature of coldest month",
    "bio12", "annual precipitation"),
  ncol = 2, byrow = TRUE
)

bbs_coef_mat <- matrix(text, ncol = 2)
rownames(bbs_coef_mat) <- name_lookup[match(bbs_cov_names, name_lookup[, 1]), 2]
colnames(bbs_coef_mat) <- c("fecundity", "survival")

@@

```{r bbs, echo = FALSE, fig.cap = "Spatial predictions from the fitted DSDM. A) Probability of presence predicted by the DSDM, with 2015 BBS presence (black dots) and absence (ringed white dots) records overlaid. B) Spatial variation in fecundity (juveniles per adult per year). C) Spatial variation in annual adult survival probability. D) The species' range limits (where $\\lambda_i \\ge 1$) under this baseline model (light blue area), a unilateral 50\\% reduction in fecundity (medium pink area overlaid) or in survival (dark green area overlaid). The predictions in panels B, C and D cannot be made using a correlative SDM.", out.width = "\\textwidth"}
knitr::include_graphics("../figures/bbs_fig.png")
```

>>>>

name_lookup <- matrix(
  c("(Intercept)", "Intercept",
    "pcMix", "Mixed forest cover",
    "pcDec", "Deciduous forest cover",
    "pcCon", "Coniferous forest cover",
    "bio1", "Annual mean temperature",
    "bio6", "Min. temperature of coldest month",
    "bio12", "Annual precipitation"),
  ncol = 2, byrow = TRUE
)

bbs_coef_mat <- matrix(text, ncol = 2)
rownames(bbs_coef_mat) <- name_lookup[match(bbs_cov_names, name_lookup[, 1]), 2]
colnames(bbs_coef_mat) <- c("fecundity", "adult survival")

@@

```{r bbs, echo = FALSE, fig.cap = "Spatial predictions from the fitted DSDM. A) Probability of presence predicted by the DSDM, with 2015 BBS presence (black dots) and absence (ringed white dots) records overlaid. B) Spatial variation in annual fecundity. C) Spatial variation in annual adult survival probability. D) The species' range limits (where the posterior probability $\\lambda_i \\ge 1$ exceeds 0.5) under this baseline model (light blue area), a unilateral 50\\% reduction in fecundity (medium pink area overlaid) or a 25\\% reduction in survival (dark green area overlaid). The predictions in panels B, C and D cannot be made using a correlative SDM.", out.width = "\\textwidth"}
knitr::include_graphics("../figures/bbs_fig.png")
```
